Experiment 4 of 4

### 2018-08-11 experiments/E_exp_3/writeup/E_exp_3.Rmd
E minor edits

```{r libs, message=FALSE}
library(knitr); library(MASS); library(ggplot2); library(lme4); library(xtable); library(plyr); library(lattice); library(LMERConvenienceFunctions); library(car); library(grid); library(lmerTest); library(reshape2); library(ggplot2); library(languageR); library(pander); source('summarySEwithin2.R')
```

@@

```{r rtlmer, cache=TRUE}
rtlmer = lmerTest::lmer(data=rtdata,
                        RT_log ~ c_Vag * c_Sel + c_Itm +
                          (1 + c_Vag * c_Sel + c_Itm | Subject))
```

```{r rtlmersummaryxtable, results='asis', cache=TRUE, echo=F}
print(xtable(summary(rtlmer)$coef, digits=c(0,2,2,1,1,4)),type='html')
```

```{r seplmersforcomparison, results='asis', cache=TRUE, echo=-3}
s1 <- subset(rtdata, subset=Selection=='Comparison')
s1lm <- lmerTest::lmer(data=s1, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(xtable(summary(s1lm)$coef, digits=c(0,2,2,1,1,4)), type='html')
```

```{r seplmersformatching, results='asis', cache=TRUE, echo=-3}
s2 <- subset(rtdata, subset=Selection=='Matching')
s2lm <- lmerTest::lmer(data=s2, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(xtable(summary(s2lm)$coef, digits=c(0,2,2,1,1,4)), type='html')
```

>>>>

```{r libs, message=FALSE}
library(knitr); library(MASS); library(ggplot2); library(lme4); library(xtable); library(plyr); library(lattice); library(LMERConvenienceFunctions); library(car); library(grid); library(lmerTest); library(reshape2); library(ggplot2); library(languageR); library(pander); source('summarySEwithin2.R')
library(kableExtra)
library(broom)
library(broom.mixed)
source("pretty_coef_table.R")
```

@@

```{r rtlmer, results='asis', cache=TRUE, echo=-2}
rtlmer = lmerTest::lmer(data=rtdata, RT_log ~ c_Vag * c_Sel + c_Itm + (1 + c_Vag * c_Sel + c_Itm | Subject))
pretty_coef_table(rtlmer, "rtlmer")
```

```{r seplmersforcomparison, results='asis', cache=TRUE, echo=-3}
s1 <- subset(rtdata, subset=Selection=='Comparison')
s1lm <- lmerTest::lmer(data=s1, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
pretty_coef_table(s1lm, "s1lm")
```

```{r seplmersformatching, results='asis', cache=TRUE, echo=-3}
s2 <- subset(rtdata, subset=Selection=='Matching')
s2lm <- lmerTest::lmer(data=s2, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
pretty_coef_table(s2lm, "s2lm")
```
